Hydras \& Co.

### 2022-09-05 doc/chapter-encoding.tex
start chapter on goedel encodings

The library \href{../theories/html/hydras.Ackermann.cPair.html}{Ackermann.cPair} defines and study Cantor's bijection from
$\mathbb{N}\times\mathbb{N}$ into $\mathbb{N}$.
Indeed the \texttt{cPair} function used in this library
 is slightly different 
     from the "usual" Cantor pairing function shown in  a big part 
     of the litterature (and Coq's standard library). 
      Since both versions are equivalent upto a swap of the 
      rguments [a] and [b], we still use  Russel O'Connors definitions and statements, mainly in order to not have to modify the order of sub-goals in long proofs.

@@

      \begin{remark}
        Compatibility with Standard lib's pairing function is stated
        by the equality \texttt{cPair $a$ $b$ = Cantor.to\_nat $(b,a)$} for any $a$ and $b$. Obviously, this swap and uncurrying of $a$ and $b$ doesn't change the fundamental properties of Cantor's pairing function.
      \end{remark}

>>>>

The library \href{../theories/html/hydras.Ackermann.cPair.html}{Ackermann.cPair} defines and study Cantor's bijection from
$\mathbb{N}\times\mathbb{N}$ into $\mathbb{N}$.
Indeed the \texttt{cPair} function used in this library
 is slightly different 
     from the "usual" Cantor pairing function shown in  a big part 
     of the litterature , and Coq's standard library \footnote{In 
\url{https://coq.inria.fr/distrib/current/stdlib/Coq.Arith.Cantor.html}}.
       Since both versions are equivalent upto a swap of the 
      rguments [a] and [b], we still use  Russel O'Connors definitions and statements, mainly in order to not have to modify the order of sub-goals in long proofs.

@@

      \begin{remark}
        Compatibility with Standard lib's pairing function
        is stated
        by the equality \texttt{cPair $a$ $b$ = Cantor.to\_nat $(b,a)$} for any $a$ and $b$. Obviously, this swap and uncurrying of $a$ and $b$ doesn't change the fundamental properties of Cantor's pairing function (being a primitive recursive bijection, monotony properties).
      \end{remark}
